Introducing an event-based architecture for concurrent and distributed evolutionary algorithms

### 2018-08-04 paper.tex
Finished changes for final version

  In this section we compare the performance of KafkEO against an implementation of
  the EvoSpace \cite{GValdez2015} pool-based architecture, using the first five
  functions of the Noiseless BBOB testbed \cite{hansen2016coco}, 
  which are real-parameter, single-objective, separable functions,
  namely: Sphere,  ellipsoidal, which is highly multimodal,
  Rastrigin,  Buche-Rastrigin,  and the purely lineal function called
  linear  slope. It is expected that the two algorithms achieve
  similar results as 
  they are functionally equivalent. The EvoSpace implementation follows the
  basic EvoSpace model in which EvoWorkers asynchronously interact with the
  population pool by taking samples of the population to perform a standard
  evolutionary search on the samples, to then return newly evolved solutions back
  to the pool.

>>>>

  In this section we compare the performance of KafkEO against an implementation of
  the EvoSpace \cite{García-Valdez2015} pool-based architecture, using the first five
  functions of the Noiseless BBOB testbed \cite{hansen2016coco}, 
  which are real-parameter, single-objective, separable functions,
  namely: Sphere,  ellipsoidal, which is highly multimodal,
  Rastrigin,  Buche-Rastrigin,  and the purely lineal function called
  linear  slope. It is expected that the two algorithms achieve
  similar results as 
  they are functionally equivalent. The EvoSpace implementation follows the
  basic EvoSpace model in which EvoWorkers asynchronously interact with the
  population pool by taking samples of the population to perform a standard
  evolutionary search on the samples, to then return newly evolved solutions back
  to the pool.
